\documentclass[12pt,a4paper]{scrartcl}
\usepackage{url, pdflscape}
\usepackage[final]{pdfpages}
\usepackage[colorlinks]{hyperref}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{makecell}
\title{Student Robotics Risk Assessment Form}

\begin{document}
\maketitle

\begin{description}
\item[Activity being assessed:] Student Robotics Competition (23 - 24 April, 2022)
\item[Location:] Southampton University Students Union (SUSU)
\item[Persons at risk:] Competitors, Team Supervisors, SR Volunteers, SUSU Staff, Visitors
\end{description}

\begin{description}
\item[Assessor's name:] Thomas Scarsbrook
\item[Responsible Persons:] Health and Safety Lead; Team Supervisors
\item[Date of assessment:] \date{\today}
\end{description}
\clearpage

%\newcommand{\risk}[4]{
%	\makecell{#1} & \makecell{#2} & \makecell{#3} & \makecell{#4} \\
%}
\newcommand{\risk}[4]{
	#1 & #2 & #3 & #4 \\
}

\begin{landscape}
\section{Risks}
The following risks have been considered for the Student Robotics Competition. 
This assessment is to be supplimented by the SUSU risk assessment.
Further description of the meaning of risk ratings (presented in this section as
$L \times S$) can be found in the final section.

\centering
\begin{longtable}{|p{17em}|p{8cm}|p{4cm}|p{4em}|}
\hline
\textbf{Hazard} & \textbf{Control Measures} & \textbf{Responsible Person} & \textbf{Risk Rating} \\
\hline
\endhead

\endfoot

\risk{Injury while using manual or power tools}
{
Tools should only be used in appropriate circumstances and in the manner they are designed to be used.
All use should be supervised by a responsible adult.
No loose clothing to be worn whilst operating power tools.
Student Robotics will not provide any tools to Competitors.
First aid provision available to manage any incidents.
}
{Health and Safety Lead, Team Supervisors}
{4}
\hline

\risk{Interaction with robots: electric shock, minor injury}
{Team Supervisors to supervise work on robots in team pits, SR Volunteers will also intervene if work seems unsafe.
Only sealed food and drink is permitted in team pit areas.}
{Health and Safety Lead, Team Supervisors}
{3}
\hline

\risk{Injury to Competitors, SR Volunteers, and Visitors due to unsafe robots}
{Robots subject to a safety inspection before entry into an arena.
Robots re-inspected randomly throughout the event, entry into the arena or access to batteries can be revoked at any time.
Anyone identifying a potential safety issue to report it to the safety inspector.
Arena access controlled by SR Volunteers - maximum of 4 teams at a time, and modification of robots inside the arena is banned (this also applies to the test arena).
Power cut off switch to be readily accessible on robots.}
{Health and Safety Lead}
{3}
\hline

\risk{Trip Hazard from trailing extension leads}
{Extension leads taped down and inspected regularly, kept away from walkways
where reasonably practicable. SR Volunteers and Team Supervisors to enforce teams
keeping within their areas and that areas are kept tidy}
{Health and Safety Lead, Team Supervisors}
{1}
\hline

\risk{Falling on stairs}
{Carrying of Robots or large or heavy objects on the stairs to be kept to a minimum. Running on the stairs is not permitted.}
{Health and Safety Lead, Team Supervisors}
{2}
\hline

\risk{Battery failure - smoke, fire}
{All batteries to be charged by trained volunteers in fire-proof bags.
Competitors and team leaders have been informed about safe use of the batteries throughout the competition year.
SR Volunteers and Team Supervisors to identify batteries showing signs of damage or swelling and deliver to Helpdesk for safe disposal.}
{Health and Safety Lead}
{4}
\hline

\risk{Injury due to objects falling from arena / arena components coming loose}
{Arena to be constructed and tested as per Method Statement, and will
be subject to inspection by SR Volunteers throughout the event, with
interventions for repair if deemed necessary.}
{Health and Safety Lead}
{3}
\hline

\risk{Injury moving robots into/out of the arena}
{Doors into arena clearly marked, and any potential trip hazards highlighted with hazard tape.
During matches, Competitors are not allowed in the arena whilst the robots are in motion.
During tinker time, robots to be switched off on entry to the arena. This will also apply to use of the test arena.
During matches robots will need to be powered up but inactive whilst entering the arena.
All robots to be powered down when exiting the arena.}
{Health and Safety Lead}
{4}
\hline

\risk{Hearing damage from excessive noise levels}
{Noise levels carefully monitored during event.}
{Health and Safety Lead}
{2}
\hline

\risk{Reaction to theatrical effects utilised, such as lighting effects}
{Flashing lights kept to a minimum.
Any flashing to be at no greater rate than 4 flashes per second.}
{Health and Safety Lead}
{4}
\hline

\risk{Accidents due to being under the influence of alcohol or drugs}
{Alcohol consumption prohibited on site. Anyone clearly under the influence will be escorted off site.}
{Health and Safety Lead}
{2}
\hline

\end{longtable}
\end{landscape}

\input{traffic-management}

\input{covid}

\input{assessment-guidance}

%\clearpage

%\newpage
%\includepdf[scale=1.0,landscape]{extras/Fire1.pdf}

\end{document}

